A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-24 paper.tex
Started on text for section 3 example - needs more work

Consider the game tree $T$ in
Figure~\ref{fig:interpolatetree}, whose edges are labelled with environment
actions.  Assume that there does not exist a partial strategy for the controller
winning against this tree and that the \textsc{findCandidate} function could
not find a candidate strategy. We choose a non-leaf node $n$ of $T$ with
maximal depth, i.e., a node whose children are leafs
(Algorithm~\ref{alg:learn}, line~3). We then split the tree at $n$ such that
both slices $T_1$ and $T_2$ contain a copy of $n$ (line~4).
Figure~\ref{fig:treef1} shows $T_1$, which contains all of $T$ except $n$'s
children, and $T_2$ (Figure~\ref{fig:treef2}), which contains only $n$ and its
children.  There is no candidate strategy for $T$ so $s \land
\textsc{treeFormula}(k, T)$ is unsatisfiable.  By construction,
$\textsc{treeFormula}(k, T) \equiv \textsc{treeFormula}(k, T_1) \land
\textsc{treeFormula}(k, T_2)$ and hence $s \land \textsc{treeFormula}(k, T_1) \land
\textsc{treeFormula}(k, T_2)$ is also unsatisfiable. This enables the construction
of an \emph{interpolant} that captures losing states at node $n$.

>>>>

Consider the game tree $T$ in
Figure~\ref{fig:interpolatetree}, whose edges are labelled with controller
actions.  There does not exist a partial strategy for the environment that is
winning against the controller actions in this tree since any requests will
always be granted. Thus the \textsc{findCandidate} function can not find a
candidate strategy. We now learn the states for which these controller actions
can force the game to stay in the controller winning set.

We choose a non-leaf node $n$ of $T$ with maximal depth, i.e., a node whose
children are leafs (Algorithm~\ref{alg:learn}, line~3). We then split the tree
at $n$ such that both slices $T_1$ and $T_2$ contain a copy of $n$ (line~4).
Figure~\ref{fig:treef1} shows $T_1$, which contains all of $T$ except $n$'s
children, and $T_2$ (Figure~\ref{fig:treef2}), which contains only $n$ and its
children.  There is no candidate strategy for $T$ so $s \land
\textsc{treeFormula}(k, T)$ is unsatisfiable.  By construction,
$\textsc{treeFormula}(k, T) \equiv \textsc{treeFormula}(k, T_1) \land
\textsc{treeFormula}(k, T_2)$ and hence $s \land \textsc{treeFormula}(k, T_1)
\land \textsc{treeFormula}(k, T_2)$ is also unsatisfiable. This enables the
construction of an \emph{interpolant} that captures losing states at node $n$.
